---
title: "Supervised Machine Learning - Predicting marks scored based on hours of study"
output: html_notebook
---

This is a simple linear regression model containing one independant variable and one dependant variables, study hours and marks scored respectively.

The model developed is used to predict marks scored if one studies for 9.25 hours.

First, importing data into the environment

```{r}
reqD<- read.csv("scores.csv")
str(reqD)
summary(reqD)
```

Splitting the required data into training and test set

```{r}
library(caTools)
set.seed(54178)
split<- sample.split(reqD$Scores,SplitRatio = 3/4)
trainS<-subset(reqD,split==TRUE)
testS<-subset(reqD,split==FALSE)
head(trainS)
head(testS)
```

Training the model using the training set of data

```{r}
ModeL<- lm(Scores~Hours,trainS)
summary(ModeL)
```

Visually represing the training model

```{r}
library(ggplot2)
library(scales)

ggplot() +
  geom_point(aes(x=trainS$Hours, y=trainS$Scores),
             colour = 'red') +
  geom_line (aes( x= trainS$Hours, y=predict(ModeL, newdata= trainS)),
             colour = 'navy') +
  ggtitle ('Hours Spent on study vs Marks scored (Training Set)') +
  xlab ('Hours spent on study') +
  ylab ('Marks scored') +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 100)) 
```

Testing the model obtained using the testing set

```{r}
NewPred <- predict(ModeL,newdata = testS)
Comparison <- as.data.frame(NewPred)
Comparison$ActualMarks<-testS$Scores
Comparison
```

Visuvalizing the linear regression model obtained for testing set

```{r}
ggplot() +
  geom_point(aes(x=testS$Hours, y=testS$Scores),
             colour = 'red') +
  geom_line (aes( x= testS$Hours, y=predict(ModeL, newdata= testS)),
             colour = 'navy') +
  ggtitle ('Hours Spent on study vs Marks scored (Testing Set)') +
  xlab ('Hours spent on study') +
  ylab ('Marks scored') +
  scale_x_continuous(limits = c(0, 10)) + 
  scale_y_continuous(limits = c(0, 100)) 
```

Plotting predicted vs actual and visuvalizing the difference

```{r}
plot(Comparison$NewPred,type= "l",lty=1.8, col="red")
lines(Comparison$ActualMarks,type = "l",lty=1.8,col="blue")
```

Predicting marks for 9.25 hours of study

```{r}
predict(ModeL,newdata = data.frame("Hours"=9.25))
```

